---
title: "notebook20160619"
author: "Mark Hagemann"
date: "June 19, 2016"
output: html_document
---

Still trying to install udunits2 package. Reinstalled udunits2 on system using Ubuntu software center. But still having configuration failure for R package.

Tying again to specify installation details. 

Actually let's try specifying environment variables.

- in .profile.

```{r}
install.packages("udunits2", configure.args = )
```

This from [install.packages documentation](https://stat.ethz.ch/R-manual/R-devel/library/utils/html/install.packages.html)

```{r}
install.packages(c("ncdf4", "RNetCDF"),@
  configure.args = c(RNetCDF = "--with-netcdf-include=/usr/bin/udunits2"))
```

Didn't work. 

Apparently I need the dev version? [says so here](http://stackoverflow.com/a/11331268).

```{r}
install.packages("udunits2")
```

OK, that worked!

```{r}
install.packages(c("ncdf", "ncdf4", "RNetCDF", "ncdf.tools"))

install.packages("ncdf4")
```

Hmm. Looks like ncdf4 requires nc-config, which may only be available when installing from source? Maybe I can just get by using RNetCDF and ncdf.tools.

```{r}
library(ncdf.tools)
library(RNetCDF)

?ncdf.tools::readNcdf #appears to actually be easier.
?RNetCDF::read.nc

foo <- readNcdf("~/Downloads/nwm.t00z.short_range.channel_rt.f004.conus.nc_georeferenced.nc")
foo <- readNcdf("~/Downloads/nwm.t06z.medium_range.channel_rt.f003.conus.nc_georeferenced.nc")
```

Error: "Not possible to detect variable name!" Try opening with RNetCDF

```{r}
nc1 <- RNetCDF::open.nc("~/Downloads/nwm.t00z.short_range.channel_rt.f004.conus.nc_georeferenced.nc")

nc2 <- read.nc(nc1)
```

That worked! It's a 'large list'.

```{r}
str(nc2, 1)
sapply(nc2, class)

nc3 <- nc2[-1] %>% 
  lapply(as.vector) %>% 
  data.frame()
str(nc3, 1)

nc3$nudge %>% as.factor %>% summary
```

todo$add("Understand, document structure of ncdf data")
todo


```{r}
glimpse(nc3)
```

Map this.

```{r}
library(leaflet)

nc3 %>% 
  sample_n(1000) %>% 
  mutate(logflow = log(streamflow)) %>% 
  summary()
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude, radius = ~logflow / max(logflow) * 5,
                   stroke = FALSE)
```

todo$add("What's with negative streamflow values?")

How is time represented in the netcdf?

```{r}
glimpse(nc3)
```

Just one snapshot time per file. 

How about size?

```{r}
pryr::object_size(nc3)
```

151 MB. So really not THAT big. 

Hardest part is going to be pulling in the requisite USGS data. todo$add("Access all usgs data for a given hour")



